Analysis of Security-Cost Trade-off of Fully Homomorphic Encryption Schemes

### 2013-06-07 Report/article.tex

\makeatletter
\newif\if@restonecol
\makeatother
\let\algorithm\relax
\let\endalgorithm\relax
\usepackage{algorithm2e}
\begin{document}

\title{Analysis of Security-Cost Trade-off of Fully Homomorphic Encryption Schemes}

@@

\maketitle
\tableofcontents

\begin{abstract}
We present a study on variants of fully homomorphic schemes and the trade-off cost/security of basic operations on bits, integers, strings... \\\\\\\\\\\\\\\\\\\\\\\\\\
\end{abstract}

@@

\section{Introduction}

(Motivation and significance of fully homomorphic encryption scheme such as Gentry's lattice-based scheme.  
This work evaluates the efficiency of FHE implementations for operations varying from XOR to sort on remote machines. Trade-off between cost and security is analyzed.) \\\\\\
A partially homomorphic encryption allows certain operations on ciphertexts such as addition or multiplication which implies a known operation on plaintext like RSA Encryption
\[\texttt{E}(\prod_{i=1}^{n}{a_i}) = \prod_{i=1}^{n}{\texttt{E}(a_i)}\] \\
then Gentry proved that there is a fully homomorphic encryption which allows both addition and multiplication on encrypted bits: 
\[\texttt{FHE}(m1) + \texttt{FHE} (m2) = \texttt{FHE}(m1+m2) \] 
\[\texttt{FHE}(m1) \times \texttt{FHE} (m2) = \texttt{FHE}(m1 \times m2) ;\ \ \ m1, m2 \in \left\{ 0, 1 \right\}\] 
\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
\section{Gentry's fully homomorphic scheme}
 FHE\\\\\\\
\subsection{The Framework}
(Overview of the algorithm and its complexity. )
In this study we use two variants of fully homomorphic encryption: 
\begin{itemize}
\item Smart-Vercauteren implementation

\item Gentry-Halevi-Smart implementation

\end{itemize}

 \\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\

\subsection{Example}
(Description using a typical operation like multiplication of two $n$-bit integers. Comparison with partial homomorphic encryption scheme such as RSA.)\\
The multipliction of two FHE-encrypted integers of n bits consists on multiplications and additions on their FHE-encrypted bits: \[(\texttt{a}_{n},\texttt{a}_{n-1}, ... ,\texttt{a}_{1}) . (\texttt{b}_{n},\texttt{b}_{n-1}, ... ,\texttt{b}_{1}) = (\texttt{r}_{2n},\texttt{r}_{2n-1}, ... ,\texttt{r}_{1})\] \\
We do $ n^{2}$ multiplications $ a_i.a_j$ and $ 2.(n + (n-1)(n-2)$ additions

\[r_1= a_1.b_1 ; c_{1,1}=0\] 
\[(r_2,c_{1,2})=\texttt{add}(a_2.b_1 ,a_1.b_2 ,c_{1,1}  ) \] 
\[(r_3,c_{2,3})=\texttt{add}(a_1.b_3,\texttt{add}( a_3.b_1, a_2.b_2 , c_{1,2} ))   \] 
 \[ \vdots    \] 
\[ (r_{n-1},c_{n-1,n-1})= ...    \] 
\[(r_{n},c_{n,n})=\texttt{add}(a_1.b_n, ...)      \] 
\[  (r_{n+1},c_{n+1,n+1})= ..   \] 
\[  \vdots      \] 
\[  (r_{2n-1},c_{2n-1,2n-1})=     \] 
\[ (r_{2n},c_{2n,2n})=  \texttt{add}(a_n.b_n, c_{2n,2n-1})    \]
So it has $O(n^{2})$ complexity. In addition to that there is the cost of key generation, encryption and decryption, and there is also the recrypt algorithm called after each addition or multiplication. On the other hand the RSA-Encryption is much more easier and has a O(1) complexity for the multiplication of n-bits integer.
\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\

\section{Experimental Evaluation of Cost}

(Describe the FHE algorithm and its corresponding implementation choice. Installation, set-up procedure and usage of the implementation. We detail the measurements to be taken, like Wall time, CPU time and memory usage based on certain security or algorithmic parameters.

Statistical analysis of the measurements using minimum, max, mean and standard deviation.) \\\\\\\\

In this section we will experimentally measure time cost of Xor-bits operations using two versions of fully homomorphic encryption programs: libScarab-1.0.0 implementing Smart-Vercauteren algorithm and HElib implementing Gentry-Halevi-Smart algorithm.
\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\

\section{Evaluation on Bench Marks}

We describe the system parameters and test vectors. This section also includes description of the process of evaluation for the following operations :

As the \textsc{hCrypt} implementation provides us with the two gates : \texttt{XOR} and \texttt{AND} which form a complete set of functional gates. The $\neg$\texttt{a} is \texttt{XOR(a,1)} while \texttt{OR(a,b)} is \texttt{XOR(XOR(a,b), AND(a,b))}.

\paragraph{ XOR of $n$-bits}

We start with the simplest operations on bits. \texttt{XOR} of $n$-bits requires $n-1$ \texttt{XOR} gates.

\paragraph{Majority of $n$-bits}

Majority bit will be evaluated with the following circuit :

\[\prod_{i=1}^{n}{a_i}+\sum_{i=1}^{n}{(\prod_{j!=i}{a_j}) \neg a_i}\]

Hence it uses $(n^2-1)$ \texttt{AND} gates and $n$ \texttt{OR} gates.

\paragraph{Sum of integers of $n$-bits} Sum of two integers can be performed using an $n$-bit adder based on \texttt{full-adder} circuits. The cost of a full adder circuit is $2$ \texttt{XOR} to calculate the sum and the cost of calculating $3-bit$ majority function for the carry.

\paragraph{Sum of arbtrary integers}

\begin{itemize}
\item Sum of : 
	\begin{itemize}
	\item  bounded integers
	\item unbounded integers
 	\end{itemize}
\item String sorting with the following methods :
	\begin{itemize}
	\item Insertion sort
	\item Merge sort
	\item Quick Sort
	\end{itemize}
\item Matrix product
\end{itemize}

Sorting is tested on a sorting network where comparator gates are used. For insertion sort we would need $n(n-1)/2$ such gates. Each comparator is designed using the following algorithm.

\restylealgo{algoruled}
\linesnumbered
\begin{algorithm}[H]
 \SetVline
 \KwData{$(a_0,a_1,\ldots, a_{n-1}$), $(b_0,b_1,\ldots, b_{n-1})$ }
 \KwResult{Return Max(a,b) and Min(a,b)}
 aIsGreater=$0$\;

 \For{$i\leftarrow n-1$ \KwTo $0$}{
     aIsGreater=aIsGreater $+\neg(b_i)a_i$ \;
 }

\For{$i\leftarrow 0$ \KwTo $n-1$}{
     $Max_i$ = aIsGreater*$a_i$ + $\neg(aIsGreater)*b_i$ \;
     $Min_i$ = $\neg(aIsGreater)*a_i$ + aIsGreater*$b_i$ \;
 }

return($(Max_0,Max_1,\ldots, Max_{n-1}$), $(Min_0,Min_1,\ldots, Min_{n-1})$)
 \caption{Comparator\label{Code:algo}}
\end{algorithm}

Each comparator gate uses $n$ \texttt{AND} gate and $n$ \texttt{OR} gates and $n$ \texttt{NOT} gates to find which one of the bit sequence is bigger and then to regenerate the maximum and the minuimum it would require $4n$ \texttt{AND} gates $2n$ \texttt{NOT} and \texttt{OR} gates.

For each operation, we provide the initial algorithm and the results obtained. Observations based on the measurements are described. 
\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\

@@

Trade-off analysis on the results obtained. Comparison with other protocols in terms of gain with security-cost trade-off. Observations and recommendations on the cost and security trade-off.\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
\section{Conclusion}
Conclusion\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
\bibliographystyle{abbrv}
\bibliography{}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\balancecolumns
% That's all folks!
\end{document}

>>>>

\makeatletter
\newif\if@restonecol
\makeatother
\let\algorithm\relax
\let\endalgorithm\relax
\usepackage{algorithm2e}

\begin{document}
\title{Analysis of Security-Cost Trade-off of Fully Homomorphic Encryption Schemes}

@@

\maketitle

\begin{abstract}
We present a study on variants of fully homomorphic schemes and the trade-off cost/security of basic operations on bits, integers, strings... 
\end{abstract}

@@

\section{Introduction(1 page)}

Partial HME, Gentry's scheme from SWHME to FHE via bootstrapping. The purpose fo FHE, the protocl in general. Remote processing of computations on encrypted input transforms a native program into another program which has a higher circuit depth. The objective of this article is to analyse the security-cost tradeoff of remote computations. The implementations that exist and the organisation of the article. With citations to the referenced articles and papers.

\section{Fully homomorphic scheme(1 page)}

A general structure of the scheme.

\subsection{Two Variants of Fully Homomorphic Encryption Scheme}

A brief description of the two FHE schemes with their algorithmic complexity of the different stages in the scheme. 
-> Smart Vercautren
-> BGV

Discuss the security of these schemes.

\subsection{Considered Implementations}

The library used, version, implementaion details, versions, references, modifications required, how-to-installl, how-to-use.Platforms accepted and other depedeices.

\subsection{Intial set-up cost(The cost not depending on the actual program)}

Can be integrated with subsection 2.1

\section{ Didactic example :  Maximum of two integer (1 page)}

\subsection{Input Program for Fully Homomorphic Encryption Scheme}

Details of the circuit or the program used to calculate the maximum of two bounded integers.

\subsection{Theoretical Cost with the Schemes}

Analyse the cost of the program wrt SV, BGV.

\subsection{Experimental Analysis}

Once for all analysis of common operations(KeyGen, Encrypt, Decrypt of 1 bit) varying the algorithmic and security parameters.

Measurements taken are CPU time, Wall Time, Memory Usage by varying the input size  and the algorithmic parameters. Noise reduction threshold.

\paragraph{KeyGen}

\paragraph{Encryption and Decryption}

\section{Choice of Benchmarks}

3 different classes of problems : 
\begin{itemize}
\item Operations on bits,
 \item operation on integers (possibility of extension on blocks and comparision with RSA and 
 \item branching
\end{itemize}

For each problem we propse the program, analyse their cost and eventually on security.

Why certain other programs cannot be executed under homomorphic encryption.

\section{Evaluation on the Benchmarks (1 page)}

Measurements on varying the parameters or the plaintext space. Evaluation of program dependent properties.

@@

Anlayze the results previously obtained and its impact on security and complexity. Comparisions of security-cost tradeoff with other schemes like RSA.
\section{Conclusion}
Conclusion\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\\
\bibliographystyle{abbrv}
\bibliography{}  % sigproc.bib is the name of the Bibliography in this case
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns
\balancecolumns
% That's all folks!
\end{document}
